### 2016-02-24 Docs/managing_jobs/managingjobs.tex
add some notes about compilers
add note about python_base

@@

@@

>>>>

\item {\em gfortran 5.3.x}: These compilers have no known issues.

@@

\subsection{PGI compilers}

The \boxlib\ floating point exception trapping is disabled with PGI compilers, due to 
problems with PGI using the system header files.

@@

Note: in order to compile, you will need to ensure that both the {\tt
python} and {\tt python\_base} modules are loaded (via the {\tt
module} command).
